---
title: "Predicting Term Deposits"
author: "MBD | ADVANCED R | June 2019"
always_allow_html: yes
output:
  html_document:
    theme: yeti
  github_document: default
params: 
  shiny: TRUE
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries, echo = FALSE, include = FALSE}
source('scripts/install_packages.R')

if (is.null(webshot:::find_phantom())) {
  webshot::install_phantomjs()
}
```

``` {r Load Prepared Data, echo = FALSE}
load('data_output/RMarkdown_Objects.RData')
```

</br>

***

## Bank Marketing Dataset  

BLABLABLAThe *Bank Marketing* dataset contains the **direct marketing campaigns of a Portuguese banking institution**. The original dataset can be found on [Kaggle](https://www.kaggle.com/henriqueyamahata/bank-marketing).  

All the files of this project are saved in a [GitHub repository](https://github.com/ashomah/Bank-Marketing).  

The dataset consists in:  

* **Train Set** with `r nrow(raw_train)` observations with `r length(raw_train)-1` features and the target `y`.  
* **Test Set** with `r nrow(raw_test)` observations with `r length(raw_test)` features. The `y` column will be added to the Test Set, with NAs, to ease the pre-processing stage.  

This project aims to predict if a customer will subscribe to a bank term deposit, based on its features and call history.  

</br>

***

## Packages  

<span style="color:red">This analysis requires these R packages:</span>  

* Data Manipulation: `data.table`, `dplyr`, `tibble`, `tidyr`  
    
* Plotting: `corrplot`, `GGally`, `ggmap`, `ggplot2`, `grid`, `gridExtra`  
    
* Machine Learning: `caret`, `dbscan`, `glmnet`, `leaderCluster`, `MLmetrics`, `ranger`, `xgboost`  

* Multithreading: `doMC`, `doParallel`, `factoextra`, `foreach`, `parallel`  

* Reporting: `kableExtra`, `knitr`, `RColorBrewer`, `shiny`, and... `beepr`.  

These packages are installed and loaded if necessary by the main script.

</br>

***
 
## Data Preparation  

The dataset is pretty clean...  

</br>

***

## Exploratory Data Analysis  

The target of this analysis is...  

</br>

***

## Data Preparation  


</br>

***

## Cross-Validation Strategy  

To validate the stability of our models, we will apply a 10-fold cross-validation, repeated 3 times.  

</br>

***

## Baseline  



</br>

***

## Feature Engineering  



</br>

***

## Feature Selection with Lasso and RFE  



</br>

***

## Tuning  


</br>

***

## Final Model  

The best model for...  

<br><br>

***

###### *Nayla Fakhoury | Martin Hofbauer | Andres Llerena | Francesca Manoni | Paul Jacques-Mignault | Ashley O'Mahony | Stavros Tsentemeidis*
###### *O17 (Group G) | Master in Big Data and Business Analytics | Oct 2018 Intake | IE School of Human Sciences and Technology*

***















