---
title: "Predicting Term Deposits"
author: "MBD | ADVANCED R | June 2019"
always_allow_html: yes
output:
  html_document:
    theme: yeti
  github_document: default
params: 
  shiny: TRUE
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries, echo = FALSE, include = FALSE}
source('scripts/install_packages.R')

if (is.null(webshot:::find_phantom())) {
  webshot::install_phantomjs()
}
```

``` {r Load Prepared Data, echo = FALSE}
#load('data_output/RMarkdown_Objects.RData')
```

</br>

***

## Bank Marketing Dataset  

The *Bank Marketing* dataset contains the **direct marketing campaigns of a Portuguese banking institution**. The original dataset can be found on [Kaggle](https://www.kaggle.com/henriqueyamahata/bank-marketing).  

All the files of this project are saved in a [GitHub repository](https://github.com/ashomah/Bank-Marketing).  

The dataset consists in:  

* **Train Set** with 17,277 observations with 19 house features, the ID, and the price.  
* **Test Set** with 4,320 observations with 19 house features and the ID. The `price` column will be added to the Test Set, with NAs, to ease the pre-processing stage.  

This project aims to predict house prices based on their features.  

</br>

***

## Packages  

This analysis requires these R packages:  

* Data Manipulation: `data.table`, `dplyr`, `tibble`, `tidyr`  
    
* Plotting: `corrplot`, `GGally`, `ggmap`, `ggplot2`, `grid`, `gridExtra`  
    
* Machine Learning: `caret`, `dbscan`, `glmnet`, `leaderCluster`, `MLmetrics`, `ranger`, `xgboost`  

* Multithreading: `doMC`, `doParallel`, `factoextra`, `foreach`, `parallel`  

* Reporting: `kableExtra`, `knitr`, `RColorBrewer`, `shiny`, and... `beepr`.  

These packages are installed and loaded if necessary by the main script.

</br>

***
 
## Data Preparation  

The dataset is pretty clean...  

</br>

***

## Exploratory Data Analysis  

The target of this analysis is...  


### Bivariate Analysis: Each Variable against Target (Y)

Let'start from the *Categorical Variables* :

#### Job
```{r, message=FALSE, warning=FALSE, echo=FALSE}

# Copy dataframe for the plots
bank_train_plot <- bank_train

mytable <- table(bank_train_plot$job, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("job", "y", "perc")

ba_job_plot <- ggplot(data = tab, aes(x = job, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Job")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_job_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Job",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```



#### Marital status

```{r, message=FALSE, warning=FALSE, echo = FALSE}

mytable <- table(bank_train_plot$marital, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("marital", "y", "perc")

ba_marital_plot <- ggplot(data = tab, aes(x = marital, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Marital")+
  ylab("Percent")+
  coord_cartesian(ylim = c(0, 1))+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_marital_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Marital",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

Single people are more likely to open a deposit. Married people are less likely. Divorced 50%-50%

#### Education

```{r, message=FALSE, warning=FALSE, echo=FALSE}
mytable <- table(bank_train_plot$education, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("education", "y", "perc")

ba_education_plot <- ggplot(data = tab, aes(x = education, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Education")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_education_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Education",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

Higher education, higher chance to open a deposit.

#### Contact

```{r, echo=FALSE, warning=FALSE, message=FALSE}

mytable <- table(bank_train_plot$contact, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("contact", "y", "perc")

ba_contact_plot <- ggplot(data = tab, aes(x = contact, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Contact")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_contact_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Contact",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

People contacted via cellular are more likely to open a deposit.

#### Month

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mytable <- table(bank_train_plot$month, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("month", "y", "perc")

ba_month_plot <- ggplot(data = tab, aes(x = month, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Month")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_month_plot
grid.text(unit(0.2, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Month",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

#### Default

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mytable <- table(bank_train_plot$default, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("default", "y", "perc")

ba_default_plot <- ggplot(data = tab, aes(x = default, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Default")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_default_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Default",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

#### Housing

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mytable <- table(bank_train_plot$housing, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("housing", "y", "perc")

ba_housing_plot <- ggplot(data = tab, aes(x = housing, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Housing")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_housing_plot
grid.text(unit(0.62, 'npc'), unit(0.97,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Housing",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```


#### Loan

```{r, echo=FALSE, message=FALSE, warning=FALSE}

mytable <- table(bank_train_plot$loan, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("loan", "y", "perc")

ba_loan_plot <- ggplot(data = tab, aes(x = loan, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Loan")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_loan_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Loan",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

Let's continue with the *numerical* variables. In order to be able to display the relationship between the variable Target(Y) and the numerical variables, the latter have been binned, in order to make the graph easier to read.

#### Age

```{r, echo=FALSE, warning=FALSE, message=FALSE}

bank_train$agebin <- cut(bank_train$age, c(20,30,35,40,50,60,100))

mytable <- table(bank_train$agebin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("age", "y", "perc")


ba_age_plot <- ggplot(data = tab, aes(x = age, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Age")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_age_plot
grid.text(unit(0.7, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Age",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

#### Balance

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$balancebin <- cut(bank_train$balance, 10)
mytable <- table(bank_train$balance, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("balance", "y", "perc")


ba_balance_plot <- ggplot(data = tab, aes(x = balance, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Balance")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_balance_plot

grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Balance",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

#### Day

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$daybin <- cut(bank_train$day, c(1,7,14,21,31))

mytable <- table(bank_train$daybin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("day", "y", "perc")


ba_day_plot <- ggplot(data = tab, aes(x = day, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Day")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_day_plot
grid.text(unit(0.7, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Day",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

#### Duration

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$durationbin <- cut(bank_train$duration, c(0,100,300,500,1000,5000))

mytable <- table(bank_train$durationbin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("duration", "y", "perc")


ba_duration_plot <- ggplot(data = tab, aes(x = duration, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Duration")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_duration_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Duration",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


#### Campaign

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$campaignbin <- cut(bank_train$campaign, c(0,2,3,5,100))


mytable <- table(bank_train$campaignbin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("campaign", "y", "perc")


ba_campaign_plot <- ggplot(data = tab, aes(x = campaign, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Campaign")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_campaign_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Campaign",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


#### Pdays

```{r,echo=FALSE, warning=FALSE, message=FALSE}

bank_train$pdaysbin <- cut(bank_train$pdays, c(-2,0,200,400,900))

mytable <- table(bank_train$pdaysbin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("pdays", "y", "perc")

ba_pdays_plot <- ggplot(data = tab, aes(x = pdays, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Pdays")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_pdays_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Pdays",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


#### Previous

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$prev_bin <- cut(bank_train$previous, c(0,3,5,60))

mytable <- table(bank_train$prev_bin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("previous", "y", "perc")

ba_previous_plot <- ggplot(data = tab, aes(x = previous, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Previous")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_previous_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Previous",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


</br>

***

## Data Preparation  


</br>

***

## Cross-Validation Strategy  

To validate the stability of our models, we will apply a 10-fold cross-validation, repeated 3 times.  

</br>

***

## Baseline  



</br>

***

## Feature Engineering  



</br>

***

## Feature Selection with Lasso and RFE  



</br>

***

## Tuning  


</br>

***

## Final Model  

The best model for...  

<br><br>

***

###### *Nayla Fakhoury | Martin Hofbauer | Andres Llerena | Francesca Manoni | Paul Jacques-Mignault | Ashley O'Mahony | Stavros Tsentemeidis*
###### *O17 (Group G) | Master in Big Data and Business Analytics | Oct 2018 Intake | IE School of Human Sciences and Technology*

***















