---
title: "Predicting Term Deposits"
author: "MBD | ADVANCED R | June 2019"
always_allow_html: yes
output:
  html_document:
    theme: yeti
  github_document: default
params: 
  shiny: TRUE
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Libraries, echo = FALSE, include = FALSE}
source('scripts/install_packages.R')

if (is.null(webshot:::find_phantom())) {
  webshot::install_phantomjs()
}
```

``` {r Load Prepared Data, echo = FALSE}
load('data_output/RMarkdown_Objects.RData')
```

``` {r Palettes, echo = FALSE}
BarFillColor <- "#330066"
HBarFillColor <- "#000099"
BarLineColor <- "#FFFAFA"
MissingColor <- "#FF6666"

color1 = 'white'
color2 = 'black'
color3 = 'black'
color4 = 'darkorchid3'
font1 = 'Impact'
font2 = 'Helvetica'
```

</br>

***

## Bank Marketing Dataset  

The *Bank Marketing* dataset contains the **direct marketing campaigns of a Portuguese banking institution**. The original dataset can be found on [Kaggle](https://www.kaggle.com/sonujha090/bank-marketing).  

All the files of this project are saved in a [GitHub repository](https://github.com/ashomah/Bank-Marketing).  

The dataset consists in:  

* **Train Set** with `r nrow(raw_train)` observations with `r length(raw_train)-1` features and the target `y`.  
* **Test Set** with `r nrow(raw_test)` observations with `r length(raw_test)` features. The `y` column will be added to the Test Set, with NAs, to ease the pre-processing stage.  

This project aims to predict if a customer will subscribe to a bank term deposit, based on its features and call history of previous marketing campaigns.  

</br>

***

## Packages  

<span style="color:red">This analysis requires these R packages:</span>  

* Data Manipulation: `data.table`, `dplyr`, `tibble`, `tidyr`  
    
* Plotting: `corrplot`, `GGally`, `ggmap`, `ggplot2`, `grid`, `gridExtra`  
    
* Machine Learning: `caret`, `dbscan`, `glmnet`, `leaderCluster`, `MLmetrics`, `ranger`, `xgboost`  

* Multithreading: `doMC`, `doParallel`, `factoextra`, `foreach`, `parallel`  

* Reporting: `kableExtra`, `knitr`, `RColorBrewer`, `shiny`, and... `beepr`.  

These packages are installed and loaded if necessary by the main script.

</br>

***
 
## Data Preparation  

The dataset is pretty clean...  

</br>

***

## Exploratory Data Analysis  

The data seems to be pretty clean with no null values and the variables being a combination of integers and factors. The dataset can be divided as follow:

###Train set

*Variables related to personal infromation of the candidate*

**Age**:The Age of the candidate. Candidates are between 18 years old and 95 years old with a mean of 41 and a median of 39. The inter-quartile range is between 33 and 48. When comparing the minimum and maximum with the interqualtile range we notice the presence of outliers.

**Job**: The Job category of the candidate. There are 12 categories of Jobs with more than half belonging to blue-collar, management and technicians, followed by admin and services. Retired candidates form 5% of the dataset, self-emplyed and entrepreneur around 6% and unemployed, housemaid and students each around 2%. The candidate with unknow jobs form less than 1%.

**marital**: The marital status of the candidate divided in 3 levels, with 60% are married, 28% are single and the rest are divorced.

** education**: The last level of edication of the candidate divided into 4 categories, 51% Secondary, 29% Tertiary , 15% primary and the remaining unknown. 

*Variables related to financial status of the candidate*
**default **: Boolean if the candiate has default, with only 1.8% of the cadidates who have defaulted.

**Balance**: The average yearly balance of the candidate in euros. The variable ranged from -8,019 to 98,417 with a mean if 1,360 and a median of 448. The data is very rightly squewed.

**housing **: Boolean if the candidate has a house loan with 55% of the candidates have one.

**loan**: Boolean if the candidate has a personal loan with 84% not having one.

*Variables related to campaign interactions with the candidate*
**contact** :Last mode of contact for the campaign, wheteher it was on the mobile phone or a landline with 65% contacted on their mobile phone.

**day**: Which day of the month was the candidate contacted with the mean and median being middle of the month.

**month**: Which month was the candidate contacted. May seems to be the peak month with 30% of the calls followed by june, july, and august.

**duration**: last phone call duration in seconds. The average call lasts around 4min however we do have the maxiumum lasting 1 hour and a half.

**campaign**: number of times the cadidate was contacted *during* this campaign. The maximum being 63 times and the minimum 1 time, which means that all the candidates were contacted and around 7% were contacted less than 3 times.

**pdays**:: number of days that passed by after the candidate was last contacted from a previous campaign. (-1 means a client was not previously contacted and this is his first campaign). Around 82% of the candidates are newly campaign clients and 7% have unkown status.The avreage time elapsed is usually more than 85days to a couple of years. 

**previous**: Number of contacts performed *before* this campaign for a candidate ranges between 0 and 58 wirh a mean less than 1. Rarely are the cases that were contacted more tahn 19 times and the majority was never contacted. 


**poutcome**: categorical variable indicating the outcome from a previous campaign whether it was successful or a failure or other and unknown.

**y**: Finally the target variable, a boolean which indicates whether the candidate has acquiered a bank term deposit account in whic we can see that 88.5% have not and only 11.5% did. This indicates that the train dataset is an unbalanced one as the positive outcome values are not representative enough. 


```{r}

summary(raw_train)
sort(summary(raw_train$job), dec=T)/nrow(raw_train)
sort(summary(raw_train$marital), dec=T)/nrow(raw_train)
sort(summary(raw_train$education), dec=T)/nrow(raw_train)
sort(summary(raw_train$default), dec=T)/nrow(raw_train)
sort(summary(raw_train$housing), dec=T)/nrow(raw_train)
sort(summary(raw_train$loan), dec=T)/nrow(raw_train)
sort(summary(raw_train$contact), dec=T)/nrow(raw_train)
sort(summary(raw_train$month), dec=T)/nrow(raw_train)
sort(summary(as.factor(raw_train$campaign),dec=T)/nrow(raw_train))
sort(summary(as.factor(raw_train$pdays),dec=T)/nrow(raw_train))
table(as.factor(raw_train$previous))
sort(summary(as.factor(raw_train$y),dec=T)/nrow(raw_train))
```

###Test set

Looking at the raw test set in which we will have to consider as our unseen data and predict the outcomer we can see that it is representitive of the train set in which the variables follow almost similar summary parameters.

```{r}
summary(raw_test)
sort(summary(raw_test$job), dec=T)/nrow(raw_test)
sort(summary(raw_test$marital), dec=T)/nrow(raw_test)
sort(summary(raw_test$education), dec=T)/nrow(raw_test)
sort(summary(raw_test$default), dec=T)/nrow(raw_test)
sort(summary(raw_test$housing), dec=T)/nrow(raw_test)
sort(summary(raw_test$loan), dec=T)/nrow(raw_test)
sort(summary(raw_test$contact), dec=T)/nrow(raw_test)
sort(summary(raw_test$month), dec=T)/nrow(raw_test)
sort(summary(raw_test(raw_train$campaign),dec=T)/nrow(raw_test))
sort(summary(raw_test(raw_train$pdays),dec=T)/nrow(raw_test))
table(as.factor(raw_test$previous))
sort(summary(as.factor(raw_test$y),dec=T)/nrow(raw_test))
```


The target of this analysis is...  

### Missings Treatment

```{r, message=FALSE, warning=FALSE, echo=FALSE}
bank_train_plot <- bank_train
BarFillColor <- "#330066"
HBarFillColor <- "#000099"
BarLineColor <- "#FFFAFA"
MissingColor <- "#FF6666"

# Palette Colour
color1 = 'white'
color2 = 'black'
color3 = 'black'
color4 = 'darkturquoise'
font1 = 'Impact'
font2 = 'Helvetica'

numcols <- c('age','balance','day','duration','campaign','pdays')
missmap(bank_train_plot[,numcols], y.labels = NULL, y.at = NULL, 
        main = 'Missing values per Numeric variable', rank.order = TRUE,
        col = c(color3, color4)) #No missing values in Numeric variables

#Numeric Variables: No missings

catcols <- c("default","housing","loan","job","marital","education","contact","month","poutcome","y")
bank_train_plot[,catcols] <- data.frame(apply(bank_train[catcols], 2, as.factor))
missmap(bank_train[,catcols], y.labels = NULL, y.at = NULL, 
        main = 'Missing values per Categorical variable', rank.order = TRUE,
        col = c(color3, color4)) #No missing values in Categorical variables
#Categorical Variables: No missings
```

### Univariate Analysis: Categorical Variables

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (i in catcols){
  if (i == 'job' | i == 'month'){
    bank_train_plot[, i] <- as.factor(bank_train_plot[,i])
    assign(paste0(i,'_factor_plot'), ggplot(bank_train_plot, aes_string(x=i)) +
           geom_bar(fill = color4)+
           theme_tufte(base_size = 5, ticks=F)+
           theme(plot.margin = unit(c(10,10,10,10),'pt'),
                 axis.title=element_blank(),
                 axis.text = element_text(colour = color2, size = 7, family = font2),
                 axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
                 legend.position = 'None',
                 plot.background = element_rect(fill = color1)))}
  else{
    bank_train_plot[, i] <- as.factor(bank_train_plot[,i])
    assign(paste0(i,'_factor_plot'), ggplot(bank_train_plot, aes_string(x=i)) +
             geom_bar(fill = color4)+
             theme_tufte(base_size = 5, ticks=F)+
             theme(plot.margin = unit(c(10,10,10,10),'pt'),
                   axis.title=element_blank(),
                   axis.text = element_text(colour = color2, size = 7, family = font2),
                   axis.text.x = element_text(hjust = 1, size = 7, family = font2),
                   legend.position = 'None',
                   plot.background = element_rect(fill = color1)))
  }
}

grid.arrange(default_factor_plot,
             housing_factor_plot,
             loan_factor_plot,
             job_factor_plot,
             marital_factor_plot,
             education_factor_plot,
             contact_factor_plot,
             month_factor_plot,
             poutcome_factor_plot,
             y_factor_plot)
```

### Univariate Analysis: Numerical Variables

```{r, message=FALSE, warning=FALSE, echo=FALSE}
#Age
age_box_plot <- ggplot(bank_train, aes(x='age', y=age)) +
                geom_boxplot(fill = color4, outlier.colour = color2, alpha=0.6)+
                coord_flip()+
                theme_tufte(base_size = 5, ticks=F)+
                theme(plot.margin = unit(c(10,10,10,10),'pt'),
                 axis.title=element_blank(),
                 axis.text = element_text(colour = color2, size = 7, family = font2),
                 axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
                 legend.position = 'None',
                 plot.background = element_rect(fill = color1))


#Balance
balance_box_plot <- ggplot(bank_train, aes(x='balance', y=balance)) +
  geom_boxplot(fill = color4, outlier.colour = color2, alpha=0.6)+
  coord_flip()+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color2, size = 7, family = font2),
        axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

#Day
day_box_plot <- ggplot(bank_train, aes(x='day', y=day)) +
  geom_boxplot(fill = color4, outlier.colour = color2, alpha=0.6)+
  coord_flip()+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color2, size = 7, family = font2),
        axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

#Duration
duration_box_plot <- ggplot(bank_train, aes(x='duration', y=duration)) +
  geom_boxplot(fill = color4, outlier.colour = color2, alpha=0.6)+
  coord_flip()+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color2, size = 7, family = font2),
        axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

#Campaign
campaign_box_plot <- ggplot(bank_train, aes(x='campaign', y=campaign)) +
  geom_boxplot(fill = color4, outlier.colour = color2, alpha=0.6)+
  coord_flip()+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color2, size = 7, family = font2),
        axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

#Pdays
pdays_box_plot <- ggplot(bank_train, aes(x='pdays', y=pdays)) +
  geom_boxplot(fill = color4, outlier.colour = color2, alpha=0.6)+
  coord_flip()+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color2, size = 7, family = font2),
        axis.text.x = element_text(hjust = 1, size = 7, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

grid.arrange(age_box_plot,
             balance_box_plot,
             day_box_plot,
             duration_box_plot,
             campaign_box_plot,
             pdays_box_plot)
```

### Bivariate Analysis: Each Variable against Target (Y)

Let'start from the *Categorical Variables* :

#### Job
```{r, message=FALSE, warning=FALSE, echo=FALSE}

# Copy dataframe for the plots
bank_train_plot <- bank_train

mytable <- table(bank_train_plot$job, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("job", "y", "perc")

ba_job_plot <- ggplot(data = tab, aes(x = job, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Job")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_job_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Job",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```



#### Marital status

```{r, message=FALSE, warning=FALSE, echo = FALSE}

mytable <- table(bank_train_plot$marital, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("marital", "y", "perc")

ba_marital_plot <- ggplot(data = tab, aes(x = marital, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Marital")+
  ylab("Percent")+
  coord_cartesian(ylim = c(0, 1))+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_marital_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Marital",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

Single people are more likely to open a deposit. Married people are less likely. Divorced 50%-50%

#### Education

```{r, message=FALSE, warning=FALSE, echo=FALSE}
mytable <- table(bank_train_plot$education, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("education", "y", "perc")

ba_education_plot <- ggplot(data = tab, aes(x = education, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Education")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_education_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Education",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

Higher education, higher chance to open a deposit.

#### Contact

```{r, echo=FALSE, warning=FALSE, message=FALSE}

mytable <- table(bank_train_plot$contact, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("contact", "y", "perc")

ba_contact_plot <- ggplot(data = tab, aes(x = contact, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Contact")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_contact_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Contact",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

People contacted via cellular are more likely to open a deposit.

#### Month

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mytable <- table(bank_train_plot$month, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("month", "y", "perc")

ba_month_plot <- ggplot(data = tab, aes(x = month, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Month")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_month_plot
grid.text(unit(0.2, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Month",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

#### Default

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mytable <- table(bank_train_plot$default, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("default", "y", "perc")

ba_default_plot <- ggplot(data = tab, aes(x = default, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Default")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_default_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Default",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```

#### Housing

```{r, echo=FALSE, message=FALSE, warning=FALSE}
mytable <- table(bank_train_plot$housing, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("housing", "y", "perc")

ba_housing_plot <- ggplot(data = tab, aes(x = housing, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Housing")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_housing_plot
grid.text(unit(0.62, 'npc'), unit(0.97,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Housing",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))
```


#### Loan

```{r, echo=FALSE, message=FALSE, warning=FALSE}

mytable <- table(bank_train_plot$loan, bank_train_plot$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("loan", "y", "perc")

ba_loan_plot <- ggplot(data = tab, aes(x = loan, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Loan")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))
ba_loan_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Loan",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

Let's continue with the *numerical* variables. In order to be able to display the relationship between the variable Target(Y) and the numerical variables, the latter have been binned, in order to make the graph easier to read.

#### Age

```{r, echo=FALSE, warning=FALSE, message=FALSE}

bank_train$agebin <- cut(bank_train$age, c(20,30,35,40,50,60,100))

mytable <- table(bank_train$agebin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("age", "y", "perc")


ba_age_plot <- ggplot(data = tab, aes(x = age, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Age")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_age_plot
grid.text(unit(0.7, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Age",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

#### Balance

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$balancebin <- cut(bank_train$balance, c(-10000,0,5000,10000,100000))
mytable <- table(bank_train$balancebin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("balance", "y", "perc")


ba_balance_plot <- ggplot(data = tab, aes(x = balance, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Balance")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_balance_plot

grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Balance",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

#### Day

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$daybin <- cut(bank_train$day, c(1,7,14,21,31))

mytable <- table(bank_train$daybin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("day", "y", "perc")


ba_day_plot <- ggplot(data = tab, aes(x = day, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Day")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_day_plot
grid.text(unit(0.7, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Day",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```

#### Duration

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$durationbin <- cut(bank_train$duration, c(0,100,300,500,1000,5000))

mytable <- table(bank_train$durationbin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("duration", "y", "perc")


ba_duration_plot <- ggplot(data = tab, aes(x = duration, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Duration")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_duration_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Duration",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


#### Campaign

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$campaignbin <- cut(bank_train$campaign, c(0,2,3,5,100))


mytable <- table(bank_train$campaignbin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("campaign", "y", "perc")


ba_campaign_plot <- ggplot(data = tab, aes(x = campaign, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Campaign")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_campaign_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Campaign",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


#### Pdays

```{r,echo=FALSE, warning=FALSE, message=FALSE}

bank_train$pdaysbin <- cut(bank_train$pdays, c(-2,0,200,400,900))

mytable <- table(bank_train$pdaysbin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("pdays", "y", "perc")

ba_pdays_plot <- ggplot(data = tab, aes(x = pdays, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Pdays")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_pdays_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Pdays",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


#### Previous

```{r, echo=FALSE, message=FALSE, warning=FALSE}

bank_train$prev_bin <- cut(bank_train$previous, c(0,3,5,60))

mytable <- table(bank_train$prev_bin, bank_train$y)
tab <- as.data.frame(prop.table(mytable, 2))
colnames(tab) <-  c("previous", "y", "perc")

ba_previous_plot <- ggplot(data = tab, aes(x = previous, y = perc, fill = y)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) + 
  theme(axis.text.x=element_text(size=10, angle=90,hjust=0.95,vjust=0.2))+
  xlab("Previous")+
  ylab("Percent")+
  theme_tufte(base_size = 5, ticks=F)+
  theme(plot.margin = unit(c(10,10,10,10),'pt'),
        axis.title=element_blank(),
        axis.text = element_text(colour = color3, size = 10, family = font2),
        axis.text.x = element_text(hjust = 1, size = 10, family = font2, angle = 45),
        legend.position = 'None',
        plot.background = element_rect(fill = color1))

ba_previous_plot
grid.text(unit(0.6, 'npc'), unit(0.9,"npc"), check.overlap = T,just = "left",
          label="Bivariate Analysis - Previous",
          gp=gpar(col=color3, fontsize=13, fontfamily = font2))

```


</br>

***

## Data Preparation  


</br>

***

## Cross-Validation Strategy  

To validate the stability of our models, we will apply a 10-fold cross-validation, repeated 3 times.  

</br>

***

## Baseline  

``` {r Baseline Results, echo=FALSE, message = FALSE, fig.align = 'center'}
all_real_results[1:3,] %>%
  rownames_to_column('Model') %>%
  mutate(
    Sensitivity = cell_spec(
      format(Sensitivity, nsmall = 7),
      color = ifelse(order(Sensitivity) <= 1, 'white', 'ghostwhite'),
      font_size = ifelse(order(Sensitivity) <= 1, 12, 11),
      background = spec_color(
        order(Sensitivity),
        option = 'D',
        begin = 0.50,
        end = 0.98,
        direction = 1
      ),
      bold = ifelse(order(Sensitivity) <= 1, TRUE, FALSE)
    )
  ) %>%
  kable(escape = FALSE, align = 'r') %>% kable_styling(bootstrap_options = c('hover', 'condensed'))
```

</br>

***

## Feature Engineering  



</br>

***

## Feature Selection with Lasso and RFE  



</br>

***

## Tuning  


</br>

***

## Final Model  

The best model for...  

<br><br>

***

###### *Nayla Fakhoury | Martin Hofbauer | Andres Llerena | Francesca Manoni | Paul Jacques-Mignault | Ashley O'Mahony | Stavros Tsentemeidis*
###### *O17 (Group G) | Master in Big Data and Business Analytics | Oct 2018 Intake | IE School of Human Sciences and Technology*

***















